Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finishing up pre nanoflare density section, draft 1

	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph. Questions to answer: why do power-law cases extend to hotter temperatures for equivalent $t_N$? Why do power-law cases show little to no deviation from IEQ?}

@@

	\par The effect of these few higher energy events can be seen where the peak temperature of event $i$ is greater than $T_{max,0}$ in the two power-law cases (blue and green curves) in the middle panel of \autoref{fig:nT_sample_profiles} 

@@

	\par\hl{Lead in with how EM ratio is better, i.e. not masquerading as a fit, just a single point; discussion of results from Brosius, how lines were chosen, then discuss histograms and types.}

@@

		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}. \textbf{Left:} Emission measure ratios separated by heating function type. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, we only show five values of $t_N$.}

@@

	\par\hl{Probably cut most of this..}
	\par The main points we emphasize from the results presented in \autoref{sec:results} are,
	\begin{enumerate}
		\item Cool emission measure slopes resulting from electron and ion heating are very similar and are well described by $\mathrm{EM}\propto T^a$. As noted in \citet{cargill_active_2014}, using the relation $Q\propto T_N^{\beta}$ yields $2\lesssim a\lesssim5$, consistent with observations.\label{itm:cool}
		\item Hot emission from electron heating results in an enhanced hot shoulder while the equivalent ion heating cases show a relatively flat peak and a steep dropoff near $10^7$ K. This effect is exacerbated as $t_N$ increases.\label{itm:hot}
		\item Hot emission due to both electron and ion heating is poorly described by the scaling $\mathrm{EM}\propto T^{-b}$. In the former, this is due to the flat hot shoulder between $10^7$ and $10^{7.5}$ K. In the latter case, the relatively flat peak and steep drop off near $10^7$ K do not allow for a power-law description of the hot emission.\label{itm:deriv}
		\item Using a power-law to describe the hot side of the $\mathrm{EM}$ distribution, single-fluid models predict less hot-emission than two-fluid models in which only the electrons are heated. In particular, for $T_N\ge4000$ s, our modified two-fluid EBTEL model predicts $3\le b\le3.5$ while the original single-fluid EBTEL model predicts $b\sim4.5$.\label{itm:histos}
		\item Including NEI does not impact the cool emission measure slope. In the case of electron heating and the single-fluid case, NEI enhances the mid-range hot $\mathrm{EM}$, but leads to a lower temperature cutoff. The emission measure distribution in the case of ion heating is unaffected. \label{itm:nei}
	\end{enumerate}
	\par We first focus on \autoref{itm:cool}. In the range $6.0\le\log{T}\le6.6$, the loop is undergoing both radiative and enthalpy-driven cooling. During this phase, the density is high and the temperature low relative to the heating and conductive cooling phase. Looking at the fourth term on the right-hand side of \autoref{eq:press_e} and \autoref{eq:col_freq}, the coupling term between the two species is roughly $\propto\bar{n}^2(\bar{T}_e-\bar{T}_i)/\bar{T}_e^{3/2}$; as density increases, so does the coupling strength. While the loop is also draining in this temperature range, the density has already increased such that $\bar{T}_e\approx\bar{T}_i$ and until the next heating event, there is nothing to drive the two species out of equilibrium. Thus, because the two-species are evolving together in this regime, we expect their emission measure distributions to be the same.
	\par In \autoref{itm:hot}, we see quite the opposite situation. In the heating and conductive cooling phases, the density is relatively low and the electron (or ion) temperature relatively high. Because the heating pulses we have used are relatively short (100 s), the heated species quickly reaches high temperatures and cools significantly by thermal conduction before Coulomb collisions can bring the two species back into equilibrium. Since the emission measure depends on the electron temperature, this means that in the event that only the electrons are heated, the emission  ``sees'' the full range of temperatures produced by heating and conductive cooling.
	\par However, in the case of ion heating, in order for the emission measure to see the full range of temperatures resulting from the heating and conductive cooling by the ions, $\bar{T}_e=\bar{T}_i$ would have to hold for this entire phase. Instead, as the ions are impulsively heated, the electrons remain at a relatively low temperature, coupled only weakly to the ions because the loop has only just begun to fill. As the coronal density increases, the electrons come into equilibrium with the ions, but because thermal conduction is such an efficient cooling mechanism in the corona, the ions have now cooled far below the temperature to which they were initially heated. 
	\par The result is a severely truncated hot emission measure distribution as seen in \autoref{fig:ion_em}. Additionally, this effect is exacerbated at long $t_N$. For short $t_N$, the heating is essentially steady, meaning that the loop has little to no time to drain or cool between heating events. This keeps the density at a roughly constant, near-equilibrium value which inhibits rapid heating to high temperatures and keeps the electrons and ions in equilibrium. However, for longer $t_N$, the loop is allowed to drain significantly between each pulse. Thus, at the start of each heating event, the density is low, allowing the species to very quickly evolve out of equilibrium. 
	\par Finally, \autoref{itm:nei} addresses the fact that NEI does not affect cool emission or emission due to ion heating, while it acts to enhance mid-range hot temperature emission and creates a lower-temperature cutoff in the single-fluid and electron heating cases as shown in \autoref{fig:teff_test_case}. As discussed in \citetalias{barnes_inference_2016} and \autoref{sec:intro}, if the heating occurs on a timescale faster than the ionization equilibration timescale, high temperatures will not be detectable because the charge states indicative of such temperatures will not have had time to form. Coolward emission is due to radiative and enthalpy-driven cooling and during this phase, the density is relatively high and the temperature is changing relatively slowly, meaning that ionization equilibrium can be assumed. 
	\par For hotward emission in the case of ion heating, we note that the effective heating timescale for the electrons is approximately $\tau_{ei}$, the coupling timescale. For $Q\approx10^{25}$ erg, the electron temperature increases relatively slowly (compared to the heating timescale of the ions) and only gets above several MK once the density has increased significantly. Thus, ionization equilibrium can be assumed because the electrons undergo no direct impulsive heating. In the cases of electron heating and the single-fluid case, the electrons undergo direct impulsive heating when the density is relatively low. This is what leads to the lower-temperature cutoff in $EM_{eff}$: at these high temperatures and low densities, the ionization equilibration timescale is significantly longer than the heating timescale and so these very high temperatures are never seen. 

@@

	\par In this paper, we have used a modified two-fluid version of the popular EBTEL model to study the effect of preferentially heating the electrons or ions on the hot and cool emission measure slopes over a parameter space that includes the power-law index describing the distribution of event energies, $\alpha$, waiting time between successive heating events, $t_N$, and the scaling between the event energy and wait time, $\beta$. We have found that while there is little difference in the cool emission between the cases of electron and ion heating, the emission measure curves of the electron-heated loops have an enhanced hot shoulder due to faster loop filling times and steepened hot mid-range slope due to accelerated cooling by the Coulomb collisions while the ion-heated loops show a truncated emission measure distribution on the hot side. These differences become more prominent as $t_N$ increases. We note that given such a distinction in the $\mathrm{EM}$ distribution between the cases of electron and ion heating, the difference could be potentially observationally diagnosable by instruments such as MaGIXS, the Focusing Optics X-ray Solar Imager (FOXSI) \citep{krucker_focusing_2011}, or other future missions with adequate spectroscopic resolution in the hard X-rays.
	\par Furthermore, by comparing these results with emission measure distributions obtained from the original single-fluid EBTEL model, we have found that heating only the electrons and using a single power-law fit leads to significantly smaller hot emission measure slopes for equivalent values of $t_N$. Thus, using a single-fluid model to interpret observed hot emission measure distributions can potentially lead to a misdiagnosis of the heating frequency. Additionally, characterizing the hotward emission with a single power-law fit, as is common practice with cool emission, does not adequately capture all of the features of the hotward emission.
	\par We note that in this study, we have constructed the most ideal emission measure curves by using the expression $\mathrm{EM}=n^2(2L)$; that is, we have not taken into account the many complications involved when computing emission measure distributions from observed spectral lines. For example, as we noted in \citetalias{barnes_inference_2016}, impulsive heating leads to NEI and a consequently lower effective temperature, meaning that the emission does not see the hottest temperatures during the conductive cooling phase. By computing test cases for electron heating, ion heating, and the single-fluid case, we have shown that NEI has the effect of steepening the hot emission measure distribution at very high temperatures and enhancing the mid-range hot temperature emission for the electron heating and single-fluid cases, but has no impact on the emission measure distribution in the case of ion heating. We stress that when interpreting observed hot emission in the context of simulation, two-fluid and non-equilibrium ionization effects should be properly taken into account in order to extract meaningful properties of the heating.

>>>>

@@

	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ power-law case is an extended cool emission measure; the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical. This provides further evidence for these two portions of the emission measure distribution being largely independent as they are determined by separate phases of the loop evolution.
	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$. Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$. From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$. In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s. So even for the lowest heating frequency in the uniform case, the heating rate is still much lower. Furthermore, for low $t_N$, between each event the loop is allowed to drain to its equilibrium value (as determined by the background heating) such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff. On the other hand, when the heating events are selected from a power-law, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times), allowing the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.

@@

@@

		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}. \textbf{Left:} Emission measure ratios separated by heating function type. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown.}

@@

@@
